Artin Group Presentations Arising from Cluster Algebras

### 2014-08-03 Presentation/Prob6.tex

\newtheorem{proposition}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{goal}{Goal}

@@

\begin{frame}
  \titlepage
  \let\thefootnote\relax\footnote{* denotes speaker}
\end{frame}

@@

\begin{frame}{Brief History}
Fomin and Zelevinsky introduced \textit{cluster algebras}, generated from seed variables. These algebras are of finite type if they are generated from a finite number of seeds. Fomin and Zelevinsky also showed that cluster algebras of finite type can be classified by Dynkin diagrams.
\begin{figure}
\centering
\includegraphics[scale = .25]{dynkindiagrams.PNG}
\caption{Dynkin diagrams}
\end{figure}
\end{frame}

\begin{frame}{Example}
\begin{figure}
\centering
\includegraphics[scale = .65]{DynkinA3.PNG}
\caption{Dynkin diagram of type $A_3$}
\end{figure}

Coxeter group relations:
\begin{itemize}
\item $s_1^2 = s_2^2 = s_3^2 = e$
\item $(s_1s_2)^3 = (s_2s_3)^3 = e$
\item $(s_1s_3)^2 = e$
\end{itemize}

Artin group relations:
\begin{itemize}
\item $\langle s_1, s_2 \rangle ^3 = \langle s_2, s_1 \rangle ^3$
\item $\langle s_2, s_3 \rangle ^3 = \langle s_3, s_2 \rangle ^3$
\item $\langle s_1, s_3 \rangle ^2 = \langle s_3, s_1 \rangle ^2$
\end{itemize}
Alternatively, the above relations correspond to 
\begin{itemize}
\item $s_1s_2s_1 = s_2s_1s_2$
\item $s_2s_3s_2 = s_3s_2s_3$
\item $s_1s_3 = s_3s_1$
\end{itemize}

\begin{frame}
Barot and Marsh extended the Coxeter group presentations to diagrams of finite type (making an allowance for chordless cycles), and proved that this group presentation is isomorphic to the Coxeter group associated to a Dynkin diagram. They also proved mutation invariance, up to isomorphism, for these Coxeter groups.

\pause
\begin{goal}
Develop variations of relations for the Coxeter group associated to a diagram of finite type provided in Barot-Marsh to define the Artin group $A_{\Gamma}$ corresponding to a diagram $\Gamma$. Prove that for $\Gamma^{\prime} = \mu_k(\Gamma)$, we get $A_{\Gamma} \cong A_{\Gamma^{\prime}}$. 
\end{goal}
\end{frame}

@@

\begin{frame}{Mutation Rules}
\begin{proposition}
[Proposition 1.4, Barot-Marsh]
Let $B$ be a $2$-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows:
\begin{itemize}
\item Reverse the orientations of all edges in $\Gamma(B)$ incident with $k$ (leaving the weights unchanged)
\item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e. with $a,b$ positive), let $c$ be the weight on the edge $j \rightarrow i$, taken to be zero if there is no such arrow. Let $c'$ be determined by $c'\geq 0$ and 
$c+c' =$ max$(a,b)$. 
Then $\Gamma(B)$ changes in a predetermined way, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.

@@

\subsection{Chordless cycles underlying $\Gamma$}

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{proposition}
[Proposition 2.1, Barot-Marsh]
Any chordless cycle in $\Gamma$ must have an unoriented structure that is one of the following. Furthermore, it must be cyclically oriented.
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{chordlesscycles.PNG}
\caption{Possible chordless cycles in a diagram}
\end{figure}

@@

\section{Coxeter group presentation (Barot-Marsh)}

@@

\begin{theorem}
[Theorem 5.4, Barot-Marsh]
\begin{enumerate}
\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
\item Let $\mathscr{A}$ be a cluster algebra of finite type. Then the groups $W_{\Gamma}$ associated to the diagrams $\Gamma$ arising from the seeds of $\mathscr{A}$ are all isomorphic (to the reflection group associated to the Dynkin diagram associated to $\mathscr{A}$).
\end{enumerate}
\end{theorem}
\end{frame}

\section{Artin group presentation (HHLP)}

@@

\section{Jacob}

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{lemma}
[Lemma 2.2, Barot-Marsh]
For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{3vertconnected.PNG}
\caption{Unoriented 3-vertex connected subdiagrams}
\end{figure}
\end{lemma}

\begin{frame}{Possible mutations for $i\--\ k\--\ j$}
\begin{corollary}
[Corollary 2.3, Barot-Marsh]
If in $\Gamma$ we have $i,j,k \in V(\Gamma), i \neq k \neq j$, and we have $i\--\ k\--\ j$, then the only possible mutations for this connected path between the three vertices are the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .40]{mutation3path.PNG}
\caption{Mutation of three connected vertices}
\end{figure}
\end{corollary}
\end{frame}

>>>>

\newtheorem{proposition}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{question}{REU Problem}

@@

\begin{frame}
  \titlepage
\end{frame}

@@

\begin{frame}{REU Problem 6}
\begin{question}
Develop variations of relations for the Coxeter group associated to a diagram of finite type provided in Barot-Marsh to define the Artin group $A_{\Gamma}$ corresponding to a diagram $\Gamma$. Prove that for $\Gamma^{\prime} = \mu_k(\Gamma)$, we get $A_{\Gamma} \cong A_{\Gamma^{\prime}}$. 
\end{question}
\end{frame}

@@

\begin{frame}{Mutation Rules}
\begin{proposition}
\cite[Proposition 1.4]{BM}
Let $B$ be a $2$-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows:
\begin{itemize}
\item Reverse the orientations of all edges in $\Gamma(B)$ incident with $k$ (leaving the weights unchanged)
\item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e. with $a,b$ positive), let $c$ be the weight on the edge $j \rightarrow i$, taken to be zero if there is no such arrow. Let $c'$ be determined by $c'\geq 0$ and 
$c+c' =$ max$(a,b)$. 
Then $\Gamma(B)$ changes in a predetermined way, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.

@@

\subsection{Unoriented structures underlying $\Gamma$}

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{proposition}
\cite[Proposition 2.1]{BM}
Any chordless cycle in $\Gamma$ must have an unoriented structure that is one of the following. Furthermore, it must be cyclically oriented.
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{chordlesscycles.PNG}
\caption{Possible chordless cycles in a diagram}
\end{figure}

@@

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{lemma}
\cite[Lemma 2.2]{BM}
For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{3vertconnected.PNG}
\caption{Unoriented 3-vertex connected subdiagrams}
\end{figure}
\end{lemma}

\begin{frame}{Possible mutations for $i\--\ k\--\ j$}
\begin{corollary}
\cite[Corollary2.3]{BM}
If in $\Gamma$ we have $i,j,k \in V(\Gamma), i \neq k \neq j$, and we have $i\--\ k\--\ j$, then the only possible mutations for this connected path between the three vertices are the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .40]{mutation3path.PNG}
\caption{Mutation of three connected vertices}
\end{figure}
\end{corollary}
\end{frame}

\section{$W_{\Gamma}$  presentation}

@@

\begin{theorem}
\cite[Theorem 5.4]{BM} 
\begin{enumerate}
\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
\item Let $\mathscr{A}$ be a cluster algebra of finite type. Then the groups $W_{\Gamma}$ associated to the diagrams $\Gamma$ arising from the seeds of $\mathscr{A}$ are all isomorphic (to the reflection group associated to the Dynkin diagram associated to $\mathscr{A}$).
\end{enumerate}
\end{theorem}
\end{frame}

\section{$A_{\Gamma}$ presentation}

@@
